---
title: "Lung Cancer"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Updating Libraries
```{r echo=T, results='hide',message=FALSE,warning=FALSE}
library(rio)
library(formattable)
library(dplyr)
library(tidyverse)
library(readxl)
library(corrplot)
library(stargazer)
library(car)
library(PerformanceAnalytics)
library(tidyr)
library(tm)
library(MASS)
library(AER)
library(ggplot2)
library(lubridate)
library(lattice)
library(lme4)
library(MuMIn)
library(ggridges)
library(hrbrthemes)
library(survival)
library(survminer)
options(scipen = 999)
```

### Importing Data Set
```{r}
df<-read_xlsx("Lung Cancer.xlsx",sheet = "Data")
str(df)
```

##Converting to factor and releveling
```{r}
df$Treatment<-as.factor(df$Treatment)

df$CellType<-as.factor(df$CellType)

#df$Status<-as.factor(df$Status)

df$Chemo<-as.factor(df$Chemo)
df$Chemo <- recode_factor(df$Chemo, "0" = "No", "10" = "Yes")
df$Treatment <- recode_factor(df$Treatment, "1" = "Standard", "2" = "New Drug")
df$CellType <- recode_factor(df$CellType, "1" = "Squamous", "2" = "Small Cell", "3" = "Adeno", "4" = "Large")
df$logDiagnosisMonths<-log(df$DiagnosisMonths)

summary(df)
```

## Checking distributions
```{r}
ggplot(df, aes(x=KarnofskyScore))+
  geom_density(color="darkblue", fill="lightblue")

ggplot(df, aes(x=DiagnosisMonths))+
  geom_density(color="darkblue", fill="lightblue")

ggplot(df, aes(x=log(KarnofskyScore)))+
  geom_density(color="darkblue", fill="lightblue")

ggplot(df, aes(x=Age))+
  geom_density(color="darkblue", fill="lightblue")

ggplot(df, aes(x=log(Age)))+
  geom_density(color="darkblue", fill="lightblue")

ggplot(df, aes(x=Survival))+
  geom_density(color="darkblue", fill="lightblue")

ggplot(df, aes(x=log(Survival)))+
  geom_density(color="darkblue", fill="lightblue")
```

## Running non-parametric model- Cell type
```{r}
y<-Surv(df$Survival,df$Status)
reg1<-survfit(formula=y~CellType,data=df)
reg1
summary(reg1)
```


```{r}
#df$Status<-as.numeric(df$Status)
ggsurvplot(fit= reg1, data=df, 
          pval = FALSE, conf.int = FALSE,
          #risk.table = TRUE, # Add risk table
          #risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#E7B800", "#2E9FDF","Red3","Coral"))
```

## Running non-parametric model- Treatment
```{r}
reg2<-survfit(formula=y~Treatment,data=df)
summary(reg2)
```


```{r}
ggsurvplot(fit= reg2, data=df, 
          pval = FALSE, conf.int = FALSE,
          #risk.table = TRUE, # Add risk table
          #risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#2E9FDF","Red3"),
          xlab="Time in days",title="Kaplan-Meier Curve for Lung Cancer Survival",
          legend.labs=c("Standard Treatment", "New Drug"), 
          legend.title="Treatment Type")
```

## Checking probablity to survive 6 months and a year
```{r}
summary(reg2,times = 365)
summary(reg2,times = 183)
```


```{r}
summary(reg2)$table
```

## Semi-parametric model - With Chemo
```{r}
reg3<-coxph(y~Treatment+CellType+Age+KarnofskyScore+DiagnosisMonths+Chemo,data=df)
summary(reg3)
```

## Model without Chemo
```{r}
reg5<-coxph(y~Treatment+CellType+Age+KarnofskyScore+DiagnosisMonths,data=df)
summary(reg5)

anova(reg3,reg5)
```

## Model without Karnofsky score
```{r}
reg6<-coxph(y~Treatment+CellType+Age+DiagnosisMonths,data=df)
summary(reg6)

anova(reg5,reg6)
```

## Assessing Propotional Hazards
```{r}
zph<-cox.zph(reg5)
zph
plot(zph)
```

```{r}
reg7<-coxph(y~Treatment+Age+DiagnosisMonths,data=df)
```

## Parametric Models
### Exponential Model
```{r}
exp<-survreg(y~Treatment+Age+DiagnosisMonths,data=df,dist = "exponential")
summary(exp)
```

### Weibull Model
```{r}
weibull<-survreg(y~Treatment+Age+DiagnosisMonths,data=df,dist = "weibull")
summary(weibull)
```

### LogLogistic Model
```{r}
LogLogistic<-survreg(y~Treatment+Age+DiagnosisMonths,data=df,dist = "loglogistic")
summary(LogLogistic)
summary(reg7)
```

```{r}
stargazer(reg7,exp,weibull,type = "text",align = TRUE,single.row=TRUE,digits=2,out = "reg.txt")
stargazer(reg7,exp,weibull,LogLogistic,type = "text",align = TRUE,single.row=TRUE,digits=2,out = "reg2.txt")
```




